---
title: "codemogProfile Gallery"
author: "Rob Kemp"
date: "July 24, 2015"
output: html_document
---

This document shows all of the charting capabilities 

```{r, echo=FALSE}
suppressMessages(suppressWarnings(library(codemogProfile)))
setwd("/opt/shiny-server/samples/sample-apps/codemog_data/")
temp = list.files(pattern="*.rdata")
myfiles = lapply(temp, load)
```

##County Map

```{r}
cp_countymap("011")
```
Geographies: County

## ACS Educational Attainment Chart
```{r}
ms_ed("011")
```
Geographies: County, Place

## ACS Educational Attainment Chart - Fewer Categories
```{r}
cp_ed_short("011")
```
Geographies: County, Place

This chart was inititally created to use in the OEDIT Blueprints 2.0 slides, but could be good in presentations.

## SDO Industry Change Chart from Peak Employment
```{r}
cp_indchange("011", "Bent")
```
Geographies: County

## SDO Industry Share Chart
```{r}
cp_jobShare("011", "Bent")
```
Geographies: County

## SDO Labor Force Age 
```{r}
cp_laborforceage("011", "Bent")
```
Geographies: County

## BLS Labor Force Size
```{r}
cp_laborforcebls("011", "Bent")
```
Geographies: County

## Net Migration by Age
```{r}
cp_migbyage("011")
```
Geographies: County

## Net Migration And New Jobs
```{r}
cp_migjobs("011", "Bent")
```
Geographies: County

## Group Quarters and Household Population
```{r}
cp_popGQ("011", "Bent")
```
Geographies: County

## Population and Component Trend Chart
```{r}
cp_poptrend("011", "Bent")
```
Geographies: County

## Census Age Distribution 2000 and 2010
```{r}
ms_census_age("011")
```
Geographies: County

## Census Household Types
```{r}
ms_hh("011")
```
Geographies: County, Place

## Census Housing Tenure Data
```{r}
ms_housing("011")
```
Geographies: County, Place

## ACS Household Income Distribution
```{r}
ms_income("011")
```
Geographies: County, Place

## SDO Jobs Time Series
```{r}
ms_jobs("011")
```
Geographies: County

## ACS Median Household Income Data
```{r}
ms_mhi("011")
```
Geographies: County, Place

## SDO Projected Population Change by Age, 2015 to 2025
```{r}
ms_popage("011")
```
Geographies: County

## Census Race Breakdown, 2000 and 2010
```{r}
ms_race("011")
```
Geographies: County, Place